Gozde and Liora Replication Code

### 2015-03-11 Gozde-Liora-Replication-Code.Rmd
figure 1 first part

@@

>>>>

# Model 2 based on glm logit

```{r}
model2 <- glm(rexvote ~ male + age1 + age2 + age4 + mye1 + mye2 + farmerown + worker + retired + unemployed + zlrs + euschlecht + zsatisdmo + disp + lfed1 + zasylumseekers + zsur + zasylumseekers:zsur + zreplacementrate + zreplacementrate:zsur + zreplacementrate:zasylumseekers + rmax + salienzmean.c + rvar.c + rvar.c:salienzmean.c + country - 1, family=binomial(link="logit"), data=data, verbose=TRUE)
summary(model2)

@@

# Figure 1 (Conditonal Effects of Unemployment and Immigration)

```{r}
library(msm)
asy <- seq(from = -.98, to=4.46, by=.01) # vector with possible values for asylumseekers
slopes <- model1$coef$fixed[17] + model1$coef$fixed[36] * asy # Estimated slopes based on estimated coefficients of unemployment (17) and unemployment x immigration (36)
estmean <- model1$coef$fixed # Estimated means for each variable 
var <- vcov(model1)
se <- rep(NA, length(asy))

for (i in 1:length(asy)) {
  j <- asy[i]
  se[i] <- deltamethod (~ (x17) + (x36)*j, estmean, var)
}

upper <- slopes + 1.96*se
lower <- slopes - 1.96*se
asy.data <- cbind(asy, slopes, upper, lower)
plot(asy, slopes, type = "l", lty = 1, ylim=c(-.2, .2), xlim=c(-2, 4), ylab= "Effect: Unemployment", xlab = "Asylumseekers", main = "The Conditional Effects of Unemployment and Immigration")
points(asy, upper, type = "l", lty = 2)
points(asy, lower, type = "l", lty = 2)
points(asy, rep(0, length(asy)), type = "l", col = "black")
```
